### 2020-10-09 paper/natastron/bblmethods.tex

@@

\end{thebibliography}

>>>>

\bibitem{m_halbwachs1986}
\bibinfo{author}{{Halbwachs}, J.~L.}
\newblock \bibinfo{title}{{Common proper motion stars in the AGK 3.}}
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics, Supplement Series}} \textbf{\bibinfo{volume}{66}},
\bibinfo{pages}{131--148} (\bibinfo{year}{1986}).

\bibitem{m_white+2013}
\bibinfo{author}{White, T.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Interferometric radii of bright {{Kepler}} stars with
	the {{CHARA Array}}: {{Cygni}} and 16 {{Cygni A}} and {{B}}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
		Society}} \textbf{\bibinfo{volume}{433}}, \bibinfo{pages}{1262}
(\bibinfo{year}{2013}).

@@

\bibitem{m_davies+2016}
\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
	planet-hosting stars using {{Bayesian}} techniques and machine learning}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
		Society}} \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183}
(\bibinfo{year}{2016}).

\bibitem{m_lund+2017}
\bibinfo{author}{Lund, M.~N.} \emph{et~al.}
\newblock \bibinfo{title}{Standing on the {{Shoulders}} of {{Dwarfs}}: The
	{{Kepler Asteroseismic LEGACY Sample}}. {{I}}. {{Oscillation Mode
			Parameters}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
\textbf{\bibinfo{volume}{835}}, \bibinfo{pages}{172} (\bibinfo{year}{2017}).
\end{thebibliography}

### 2020-10-09 paper/natastron/bblpaper.tex

@@

@@

@@

\bibitem{dalton+2014}
\bibinfo{author}{Dalton, G.} \emph{et~al.}
\newblock \bibinfo{title}{Project overview and update on {{WEAVE}}: The next
  generation wide-field spectroscopy facility for the {{William Herschel
  Telescope}}} \textbf{\bibinfo{volume}{9147}}, \bibinfo{pages}{91470L}
  (\bibinfo{year}{2014}).
\end{thebibliography}

>>>>

	\bibitem{barnes+2016}
	\bibinfo{author}{Barnes, S.~A.}, \bibinfo{author}{Weingrill, J.},
	\bibinfo{author}{Fritzewski, D.}, \bibinfo{author}{Strassmeier, K.~G.} \&
	\bibinfo{author}{Platais, I.}
	\newblock \bibinfo{title}{Rotation {{Periods}} for {{Cool Stars}} in the 4
		{{Gyr}} old {{Open Cluster M67}}, {{The Solar}}-{{Stellar Connection}}, and
		the {{Applicability}} of {{Gyrochronology}} to at least {{Solar Age}}}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
	\textbf{\bibinfo{volume}{823}}, \bibinfo{pages}{16} (\bibinfo{year}{2016}).

@@

	\bibitem{metcalfe+2016}
	\bibinfo{author}{Metcalfe, T.~S.}, \bibinfo{author}{Egeland, R.} \&
	\bibinfo{author}{{van Saders}, J.}
	\newblock \bibinfo{title}{Stellar {{Evidence That}} the {{Solar Dynamo May Be}}
		in {{Transition}}}.
	\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Letters}}
	\textbf{\bibinfo{volume}{826}}, \bibinfo{pages}{L2} (\bibinfo{year}{2016}).

@@

	\bibitem{reinhold+2020}
	\bibinfo{author}{{Reinhold}, T.} \emph{et~al.}
	\newblock \bibinfo{title}{{The Sun is less active than other solar-like
			stars}}.
	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{368}},
	\bibinfo{pages}{518--521} (\bibinfo{year}{2020}).
	\newblock \eprint{2005.01401}.

@@

	\bibitem{dalton+2014}
	\bibinfo{author}{Dalton, G.} \emph{et~al.}
	\newblock \bibinfo{title}{Project overview and update on {{WEAVE}}: The next
		generation wide-field spectroscopy facility for the {{William Herschel
				Telescope}}} \textbf{\bibinfo{volume}{9147}}, \bibinfo{pages}{91470L}
	(\bibinfo{year}{2014}).

	\bibitem{blanton+2019}
	\bibinfo{author}{{Blanton}, M.} \emph{et~al.}
	\newblock \bibinfo{title}{{The Sloan Digital Sky Survey as an Archetypal
			Mid-Scale Program}}.
	\newblock In \emph{\bibinfo{booktitle}{Bulletin of the American Astronomical
			Society}}, vol.~\bibinfo{volume}{51}, \bibinfo{pages}{196}
	(\bibinfo{year}{2019}).

	\bibitem{kollmeier+2019}
	\bibinfo{author}{{Kollmeier}, J.} \emph{et~al.}
	\newblock \bibinfo{title}{{SDSS-V Pioneering Panoptic Spectroscopy}}.
	\newblock In \emph{\bibinfo{booktitle}{Bulletin of the American Astronomical
			Society}}, vol.~\bibinfo{volume}{51}, \bibinfo{pages}{274}
	(\bibinfo{year}{2019}).

\end{thebibliography}

### 2020-10-09 paper/natastron/methods.tex

In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting. The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.

@@

	In practice, the model would still properly fit a spectrum where this kind of mode-overlapping occurred, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime. A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlapped with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.

@@

Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution.

@@

This work made use of publicly available data described in the text, and reiterated here. \kepler power spectral density  were obtained from the \href{http://kasoc.phys.au.dk/}{KASOC} webpages for the majority of stars, and from the \href{https://archive.
		stsci.edu/prepds/kepseismic/}{MAST} for 16 Cyg A and B. This work used asteroseismic data from Silva Aguirre et al. (2015, 2017), Davies et al. (2016) and Lund et al. (2017) \cite{silvaaguirre+2015, davies+2016, lund+2017, silvaaguirre+2017 }. Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al. (2020) \cite{berger+2020}.\\

>>>>

In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting. The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985} and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.

@@

	In practice, the model still properly fits a spectrum where this kind of mode-overlapping occurred, as the $\ell = 0$ modes don't split, meaning that there are no degenerate solutions in this regime, and further constraints can be obtained from the other modes and split components in the spectrum. A more serious issue may be when the $\ell = 1$ mode at lower frequencies overlapped with the $\ell = 2$ mode as well, which would only occur at a rotation rate of 2 days or faster for the star with the smallest $\delta\nu_{01}$.

@@

Second, the binary pairs of KIC 9139151 \& 9139163 and 16 Cyg A \& B are individually observed binary components with wide orbital separations, so we do not expect their binarity to have affected their rotational evolution \cite{m_halbwachs1986, m_white+2013}.

@@

This work made use of publicly available data described in the text, and reiterated here. \kepler power spectral density  were obtained from the \href{http://kasoc.phys.au.dk/}{KASOC} webpages for the majority of stars, and from the \href{https://archive.
		stsci.edu/prepds/kepseismic/}{MAST} for 16 Cyg A and B. This work used asteroseismic data from Silva Aguirre et al. (2015, 2017), Davies et al. (2016) and Lund et al. (2017) \cite{m_silvaaguirre+2015, m_silvaaguirre+2017,m_davies+2016, m_lund+2017}. Parameter distributions of the \kepler field used to alter our stellar population models were taken from Berger et al. (2020) \cite{m_berger+2020}.\\
